### 2014-03-22 paper/paper.tex
Paper has twonormals image and goes until Technique section of linear stuff

\section*{Introduction}
Determining the similarity of two items is super important because... With large
amounts of rating data, collaborative filtering is a good method for
calculating similarity. However, with sparse rating data, this
technique gives noisy and unreliable approximations for similarity. Even worse, 
low confidence measurements of similarity are indistinguishable from high
confidence ones. In this paper, we develop a novel method which incorporates
confidence into the similarity score to produce more accurate estimates of
similarity.

@@

There are a few ways to compute the similarity of two vectors. One approach is
to use Cosine-similarity, defined as the cosine of the angle between the two vectors:
\begin{align}
PearsSim(A, B) = ...
\end{align}
where this = that ... Another popular approach is to use Pearson correlation:
\begin{align}
CosSim(A, B) = ...
\end{align}
where this = that.  Other similarity functions exist, such as one-sided similarities, but Pearson
correlation and Cosine-similarity are the most popular and will be the two
measurements used in this paper. \footnotemark

@@

\section*{Model}
We model the problem probabilistically. Let $Y$ be a random variable
representing the $TrueSim$ of a randomly chosen pair of items. Let $X_n$ be a
random variable representing the $Sim$ of a pair of items with $n$ common users.

@@

\begin{itemize}
    \item illustration
\end{itemize}

@@

\begin{itemize}
    \item MLE with bias
    \item Features - linear, mu is fixed point
    \item Slope - between 0 and 1. As sigma2 changes. 
    \item Model sigma2 as a function of users in common
    \item Show final parameterized model - discuss params, speculation in model (?)
\end{itemize}

>>>>

\section*{Introduction}
The similarity of two items is a valuable measurement for a number of
data-mining applications, such as recommender systems. With large
amounts of rating data, collaborative filtering is a good method for
calculating similarity. However, with sparse rating data, this
technique gives noisy and unreliable approximations for similarity. Even worse, 
low confidence measurements of similarity are indistinguishable from high
confidence ones. In this paper, we develop a novel method which incorporates
confidence into the similarity score to produce more accurate estimates of
similarity.

@@

There are a few ways to compute the similarity of two vectors. One approach is
to use Cosine-similarity, defined as the cosine of the angle between the two vectors:
\begin{align}
CosSim(A, B) = \frac{\sum\limits_{u\in U_{AB}}
r_{u,A}r_{u,B}}{\sqrt{\sum\limits_{u\in U_{A}} r_{u,A}^2}
\sqrt{\sum\limits_{u\in U_{B}} r_{u,B}^2}}
\end{align}
where $U_{I}$ is the set of all users who rated item $I$, $U_{AB}$ is the set of all 
users who rated both item $A$ and item $B$ and $r_{u,I}$ is the rating user $u$ gave 
to item $I$. Another popular approach is to use Pearson correlation:
\begin{align}
PearsSim(A, B) = \frac{\sum\limits_{u\in U_{AB}}
r_{u,A}r_{u,B}}{\sqrt{\sum\limits_{u\in U_{AB}} r_{u,A}^2}
\sqrt{\sum\limits_{u\in U_{AB}} r_{u,B}^2}}
\end{align}
Other similarity functions exist, such as one-sided similarities, but Pearson
correlation and Cosine-similarity are the most popular and will be the two
measurements used in this paper. \footnotemark

@@

\section*{Model}
We model the problem probabilistically. Let $Y$ be a random variable
representing the $TrueSim$ of a randomly chosen pair of items. Let $X_n$ be a
random variable representing the calculated $Sim$ of a pair of items with $n$ common users.

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.5\textwidth]{twonormals.png}
    \caption{The blue curve represents $Y$, the distribution of true similarities
    between a random pair of items. The red curve represents $X|Y$, the
    estimated similarity when a small number of common users exist.}
    \label{fig:two_normals}
\end{figure}

@@

The model suggests that there is a linear correlation between $X_n$, the
similarity calculated with $n$ common users, and $Y$, the true similarity. Since 
$\sigma_{2,n}^2\ge0$, the slope is always $\le1$, meaning that the calculated
distance from $\mu$ (the average similarity) overestimates the true distance. This makes
sense, since there is a prior distribution of true similarity weighted around $\mu$.

The parameters $\mu$, $\sigma_{1}^2$, and $\sigma_{2,n}^2$ all can be approximated 
using the method of moments over training data where there are enough common
users that $TrueSim$ can be approximated. This method requires approximating
$\sigma_{2,n}^2$ for every value of $n$ separately. Alternatively, we can model
$\sigma_{2,n}^2$ as a function of $n$. Recall that $\sigma_{2,n}^2$ is the
noisiness of the measurement $Sim$ about $TrueSim$ and $TrueSim = lim_{n \to
\infty}Sim$. Thus $Sim$ can be thought of as a sampling $n$ users from the
infinite set used to calculate $TrueSim$. Although $Sim$ may not be linear, we
the Central Limit Theorem motivates the intuition that the variance of $Sim$
would decrease as the $sqrt(n)$. Thus we model $\sigma_{2,n}^2$ as:

\begin{align}
\sigma_{2,n}^2 = \frac{\alpha}{\sqrt{n}}
\end{align}
Yielding the single parameter model:
\begin{align}
\left(Y - \mu\right) = \frac{\sigma_{1}^2}{\sigma_{1}^2+\frac{\alpha}{\sqrt{n}}}
\left(X_n-\mu\right)
\end{align}
In terms of a modified similarity function, as desired earlier, we now have:
\begin{align}
ModSim(Sim, n) = \frac{\sigma_{1}^2}{\sigma_{1}^2+\frac{\alpha}{\sqrt{n}}}
\left(Sim-\mu\right) + \mu
\end{align}
